Writing Trash Bin

### 2024-02-12 writingdumpster.qmd
finished similar work section and moved it to be beneath the introduction

---
title: "Writing Trash Bin"
author: "Harriet Mason"
format: html
---
# Why this exists
I have an information hoarding problem, this helps me throw out sections of the literature review that are not necessarily relevant without actually throwing it out. Knowing that I can come back to this at any point and pull information back, makes me more comfortable with removing it from the report.
# Definition outtakes
## Random
- mentions uncertainty can be variance, precision, accuracy, reliability, or related concepts @Hullman2016
-  @Spiegelhalter2017 defines risk as risk known probabilities and uncertainty as estimated probabilities, therefore uncertainty is what we have when you cannot accurately quantify risk.

>>>>

---
title: "Writing Trash Bin"
author: "Harriet Mason"
format: html
---
# Why this exists
I have an information hoarding problem, this helps me throw out sections of the literature review that are not necessarily relevant without actually throwing it out. Knowing that I can come back to this at any point and pull information back, makes me more comfortable with removing it from the report.

# Moved over notes
- mentions uncertainty can be variance, precision, accuracy, reliability, or related concepts @Hullman2016
-  @Spiegelhalter2017 defines risk as risk known probabilities and uncertainty as estimated probabilities, therefore uncertainty is what we have when you cannot accurately quantify risk.
